---
title: "KD Joins 30K Club"
author: "Davide Tissino"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = F)
```
The following document is an attempt at creating a career overview of a specific player -- in this case Kevin Durant -- on the basis of the points he scored during his career. In the future, an effort will be made at focusing such type of analysis also on other stats, to better render players' career stats.

Specifically, along this script we will develp several differnt graphs, each with a specific focus: 

- The first graph will highlight the total amount of points scored by the player during each NBA Regular Season of his career; specifically, the plot will divided along three dimensions corresponding to the type of Field Goal (2PT or 3PT) or Free Throw that generated the relevant amount of points. 


We will begin by loading a series of standard packages required along the various steps of our analysis, as well as setting the appropriate conditions to perform scaraping of NBA stats

```{r, echo = T}
# Initial setup
library(ggthemes)
library(extrafont)
library(tidyverse)
library(nbastatR)
library(jsonlite)
library(httr)
library(prismatic)
library(ggimage)
library(tictoc)
library(sportyR)
library(ggtext)
library(geomtextpath)
library(stringi)
library(knitr)

## Create various graphs for career points overview of specific player
## Graph 1: YoY PTS scored progression, divided in 2pt, 3pt and ft


# headers Ryan Davis (?)
headers <- c(
  `Connection` = 'keep-alive',
  `Accept` = 'application/json, text/plain, */*',
  `x-nba-stats-token` = 'true',
  `X-NewRelic-ID` = 'VQECWF5UChAHUlNTBwgBVw==',
  `User-Agent` = 'Mozilla/5.0 (Macintosh; Intel Mac OS X 10_14_6) AppleWebKit/537.36 (KHTML, like Gecko) Chrome/78.0.3904.87 Safari/537.36',
  `x-nba-stats-origin` = 'stats',
  `Sec-Fetch-Site` = 'same-origin',
  `Sec-Fetch-Mode` = 'cors',
  `Referer` = 'https://stats.nba.com/players/shooting/',
  `Accept-Encoding` = 'gzip, deflate, br',
  `Accept-Language` = 'en-US,en;q=0.9'
)

# buffer size
Sys.setenv("VROOM_CONNECTION_SIZE"= 131072 * 10)


## CUSTOM THEME ####
theme_davide <- function() {
  theme_fivethirtyeight(base_family = 'avenir') %+replace%  
    theme(
      text = element_text(family='avenir'), 
      panel.background = element_rect('floralwhite'), 
      plot.background = element_rect('floralwhite'),
      plot.title = element_text(size=22, hjust=.5, vjust = -3, face = 'bold'),
      plot.subtitle = element_text(size=12, vjust=-8.5, face = 'italic'), 
      plot.margin = margin(0, 0, 0, 0, "cm"), 
      panel.grid.major = element_line(color='floralwhite')
    ) 
}
```

<!--- GRAPH 1 --->

## When Were Points Scored 

The section will start by deriving relevant information regarding the player's career stats. We begin by filtering our Active Players Index according to the desired player's name. 

```{r}
# Setup: set player name 
input_player <- 'Kevin Durant'

```



```{r}
# derive player index data
player_index <- players %>% 
  filter(
    Player == input_player
  )


# derive player ID 
player_ID <- players$idPlayer[players$Player == input_player]
```

```{r}
player_index
```

```{r table, results = 'asis'}
kable(player_index[, c(2, 4, 6, 8:11)], 
      caption = 'Resulting Knitr Table')
```





```{r}
## Scrape Career Stats ====

url <- paste0(
  'https://stats.nba.com/stats/playercareerstats?LeagueID=00&PerMode=Totals&PlayerID=', 
  player_ID
)

res <- GET(url = url, add_headers(.headers=headers))
json_resp <- fromJSON(content(res, "text"))


#### Regular Season Year by Year ----
RS_yoy <- data.frame(json_resp$resultSets$rowSet[1])
colnames(RS_yoy) <- json_resp[["resultSets"]][["headers"]][[1]]  

```




```{r}

clean_career_YoY <- RS_yoy %>%
  arrange(
    PLAYER_ID, 
    SEASON_ID, 
    TEAM_ID != 0, 
    TEAM_ID) %>%  # Ensure latest team is above TOT
  group_by(
    PLAYER_ID, 
    SEASON_ID) %>%
  mutate(
    TEAM_ABBREVIATION = ifelse(
      TEAM_ABBREVIATION == "TOT", 
      last(
        TEAM_ABBREVIATION[TEAM_ID != 0]
        ), 
      TEAM_ABBREVIATION
      )
    ) %>%
  filter(
    !(TEAM_ID != 0 & any(TEAM_ID == 0))
    ) %>%  # Remove partials if a TOT row exists
  ungroup()


```


```{r}
ses <- RS_yoy %>%
  arrange(PLAYER_ID, SEASON_ID, TEAM_ID != 0, TEAM_ID) %>%  # Ensure correct ordering
  group_by(PLAYER_ID, SEASON_ID) %>%
  mutate(
    # Update the TEAM_ID and TEAM_ABBREVIATION for the TOT row
    TEAM_ID = ifelse(TEAM_ABBREVIATION == "TOT", last(TEAM_ID[TEAM_ID != 0]), TEAM_ID),
    TEAM_ABBREVIATION = ifelse(TEAM_ABBREVIATION == "TOT", last(TEAM_ABBREVIATION[TEAM_ID != 0]), TEAM_ABBREVIATION)
  ) %>%
  filter(!(TEAM_ID != 0 & any(TEAM_ID == 0))) %>%  # Remove partials but keep TOT
  ungroup()

```




```{r}
ses <- RS_yoy %>%
  group_by(PLAYER_ID, SEASON_ID) %>%
  # Update the TOT row with the latest team the player played for
  mutate(
    TEAM_ID = ifelse(TEAM_ABBREVIATION == "TOT", last(TEAM_ID[TEAM_ID != 0]), TEAM_ID),
    TEAM_ABBREVIATION = ifelse(TEAM_ABBREVIATION == "TOT", last(TEAM_ABBREVIATION[TEAM_ID != 0]), TEAM_ABBREVIATION)
  ) %>%
  # Filter out partial rows and keep only the TOT row
  filter(!(TEAM_ID != 0 & TEAM_ABBREVIATION != "TOT" & lead(TEAM_ABBREVIATION) == "TOT")) %>%
  ungroup()


```





###### RS YoY ====

# Create df with PTS scored overview (2pt, 3pt, ft)

RS_yearly <- RS_yoy %>% 
  mutate_at(
    c(10, 13), 
    as.numeric
  ) %>% 
  mutate(
    FG2M = FGM - FG3M
  ) %>%
  select(
    SEASON_ID, 
    FG2M, 
    FTM, 
    FG3M,
    PTS) %>%
  mutate(
    FG2PTs = as.numeric(FG2M * 2),
    FG3PTs = FG3M * 3,
    FTPTs = as.numeric(FTM)
  ) %>%
  select(
    SEASON_ID, 
    FG2PTs, 
    FG3PTs, 
    FTPTs, 
    PTS) %>% 
  pivot_longer(
    c("FG2PTs","FTPTs","FG3PTs"), 
    names_to="shot_type", 
    values_to="shot_points") %>%
  mutate(
    shot_type = factor(shot_type, levels=c("FG2PTs","FTPTs","FG3PTs")), 
    shot_lab = case_when(
      shot_type == "FG2PTs" ~ "Points From 2 PT Field Goal",
      shot_type == "FG3PTs" ~ "Points From 3 PT Field Goal",
      shot_type == "FTPTs" ~  "Points From Free Throw")
  )



# Plot all PTS YoY with three lines (2pt, 3pt, ft)
ggplot(data = RS_yearly, aes(x=SEASON_ID, y=shot_points, group=shot_type))+
  geom_segment(
    aes(
      x=SEASON_ID, 
      xend=SEASON_ID,
      y=0, 
      yend=max(shot_points)+10, 
      color='black'
    ), 
    linewidth=.7, 
    linetype="dotted", 
    alpha=.3)+
  geom_textbox(
    aes(
      y=max(shot_points)+150,
      label = 'SAMOS',
      color='black'), 
    box.color=NA, 
    fill=NA, 
    hjust=.5, 
    halign=.5, 
    lineheight=.8, 
    alpha=.2) +
  geom_textbox(
    data = RS_yearly %>% 
      filter(shot_points == max(shot_points)), 
    aes(y=max(shot_points)+150,
        label = 'SUS',
        color='black'), 
    box.color=NA, 
    fill=NA, 
    hjust=.5, 
    halign=.5, 
    lineheight=.8)+
  geom_area(
    aes(fill=shot_type),
    linewidth=1.5,
    alpha=.2, 
    position="identity") +
  scale_fill_manual(values=c("#e63946","#ee9b00","#00afb9","#f35345" ))+
  theme_minimal()+
  scale_color_identity()+
  geom_textline(aes(label=shot_lab, color=shot_type), family="Open Sans", fontface=2, linewidth=1.5, hjust=.2,text_smoothing = 50, size=5)+
  scale_color_manual(values=c("#e63946","#ee9b00","#00afb9", "#f35345"))+
  theme(legend.position="none",
        axis.text = element_blank(),
        axis.title = element_blank(),
        axis.ticks = element_blank(),
        axis.text.y = element_text(color="#A2A2A2", face="bold"))+
  coord_cartesian(clip="off")



