---
title: "R Markdown Trial"
author: "Davide Tissino"
date: "2025-02-12"
output: html_document
---


Initial Setup: 

<!-- need one line of space otherwise does not create list -->
- use include = F to prevent code AND result from appearing
- use echo = F to prevent code BUT not result from appearing

```{r setup, include=FALSE}
knitr::opts_chunk$set(include = TRUE)   # allows code and result 
```

### Starting Out

The purpose of this document is to contain 

```{r, include = FALSE}
# Required Libraries
library(httr)
library(jsonlite)
library(knitr)

# Load headers to scrape 
headers <- c(
  `Connection` = 'keep-alive',
  `Accept` = 'application/json, text/plain, */*',
  `x-nba-stats-token` = 'true',
  `X-NewRelic-ID` = 'VQECWF5UChAHUlNTBwgBVw==',
  `User-Agent` = 'Mozilla/5.0 (Macintosh; Intel Mac OS X 10_14_6) AppleWebKit/537.36 (KHTML, like Gecko) Chrome/78.0.3904.87 Safari/537.36',
  `x-nba-stats-origin` = 'stats',
  `Sec-Fetch-Site` = 'same-origin',
  `Sec-Fetch-Mode` = 'cors',
  `Referer` = 'https://stats.nba.com/players/shooting/',
  `Accept-Encoding` = 'gzip, deflate, br',
  `Accept-Language` = 'en-US,en;q=0.9'
)

```

Now it is sufficient to create a simple function to scrape all NBA players' boxscores for a specific Regular Season. The function will look like the following: 

```{r scrape}

# function returning ALL individual gamelogs for the season
gamelogs <- function(season) {
  
  url <- paste0('https://stats.nba.com/stats/leaguegamelog?Counter=1000&DateFrom=&DateTo=&Direction=DESC&ISTRound=&LeagueID=00&PlayerOrTeam=P&Season=', 
                season, '&SeasonType=Regular%20Season&Sorter=DATE')
  
  res <- GET(url = url, add_headers(.headers = headers))
  resp <- fromJSON(content(res, 'text'))
  
  logs <- data.frame(resp$resultSets$rowSet)
  colnames(logs) <- resp[['resultSets']][['headers']][[1]]
  
  return(logs)
  }
```

Having developed a function to scrape all box-scores for a specific Season, it is sufficient to call the function for our Regular Season of interest, which in this case is the 2024-25 NBA Regular Season. Note that when referencing a specific RS, we will call the function as year - 1:

```{r logs, include = T}
# to call the function for RS 2024-25:
logs23 <- gamelogs(2024)
```

Which will look something like this (reduced the dataframe to only some rows and columns for reference): 

```{r table, results = 'asis', echo = F}
kable(logs23[c(1:5), c(3, 5, 8:10)], 
      caption = 'Resulting Knitr Table')
```







